Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-07-16 gtsummary_submission.tex
overleaf

The \code{tbl\_regression()} function leverages the huge effort behind the \pkg{broom} and \CRANpkg{broom.helpers} packages to perform the initial formatting of the regression object \citep{broom}\citep{broom.helpers}.
Because \code{tbl\_regression()} utilizes \code{broom::tidy()}, there are many model types that are supported out of the box, such as \code{lm()}, \code{glm()}, \code{lme4::lmer()}, \code{lme4::glmer()}, \code{geepack::geeglm()}, \code{survival::coxph()}, \code{survival::survreg()}, \code{survival::clogit()}, \code{nnet::multinom()}, \code{rstanarm::stan\_glm()}, models built with the \pkg{mice} package \citep{mice}, and many more.
A custom tidier may be specified as well, which is helpful when you need to present non-standard modifications to your model results such as Wald confidence intervals or results with modified variance-covariance standard errors.

>>>>

The \code{tbl\_regression()} function leverages the huge effort behind the \pkg{broom} and \CRANpkg{broom.helpers} packages to perform the initial formatting of the regression object \citep{broom,broom.helpers}.
Because \code{tbl\_regression()} utilizes \code{broom::tidy()}, there are many model types that are supported out of the box, such as \code{lm()}, \code{glm()}, \code{lme4::lmer()}, \code{lme4::glmer()}, \code{geepack::geeglm()}, \code{survival::coxph()}, \code{survival::survreg()}, \code{survival::clogit()}, \code{nnet::multinom()}, \code{rstanarm::stan\_glm()}, models built with the \pkg{mice} package \citep{mice}, and many more.
A custom tidier may be specified as well, which is helpful when you need to present non-standard modifications to your model results such as Wald confidence intervals or results with modified variance-covariance standard errors.
